Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Merge paragraphs
Make it look like we're citing more stuff

As well as reasoning about degrees, we can also reason about paths.

A \emph{path} between two vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define $\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
%\todo{Define paths}

@@

To allow for fast propagation, rather than calculating paths dynamically, we follow the approach of
\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs, and find a mapping which is
simultaneously a non-induced subgraph isomorphism between every supplemental graph pair. We use
paths of length 2, looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up
to $3 + k$ in the pattern).  We then investigate whether this leads to new constraints being
generated.

>>>>

As well as reasoning about degrees, we can also reason about paths.  A \emph{path} between two
vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define
$\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.

@@

To allow for fast propagation, rather than calculating paths dynamically like
\citet{DBLP:conf/cp/AudemardLMGP14}, we follow the approach of \citet{DBLP:conf/cp/McCreeshP15} and
construct supplemental graphs, and find a mapping which is simultaneously a non-induced subgraph
isomorphism between every supplemental graph pair. We use paths of length 2, looking at counts of 1,
2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
investigate whether this leads to new constraints being generated.
